### 2020-03-25 supp.tex
consistency

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_R_t_all.pdf}
\caption{
\textbf{Comparison of effective reproduction number and the daily number of reported cases in Daegu, Seoul, Gyeongsangbuk-do, and Gyeonggi-do.}
}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_R_t_seoul_linelist.pdf}
\caption{
\textbf{Comparison of effective reproduction number in Seoul using the number of reported cases by the KCDC and the line list provided by the Seoul Metropolitan Government.}
Using line list, we reconstructed incidence for local $I_t^{\textrm{local}}$ and imported $I_t^{\textrm{imported}}$ cases separately based on the method described in the main text. Then, we estimated the time-dependent reproduction number via $\mathcal R_t = I_t^{\textrm{local}}/\sum_{k=1}^{14} I_{t-k} w_k$, where $I_t=I_t^{\textrm{local}}+I_t^{\textrm{imported}}$. We did not account for changes in testing criteria in this analysis.
The line lists were obtained from \url{http://news.seoul.go.kr/welfare/archives/513105}.
}
\end{figure}

>>>>

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_R_t_all.pdf}
\caption{
\textbf{Comparison of time-dependent reproduction number and the daily number of reported cases in Daegu, Seoul, Gyeongsangbuk-do, and Gyeonggi-do.}
}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{figure_R_t_seoul_linelist.pdf}
\caption{
\textbf{Comparison of time-dependent reproduction number in Seoul using the number of reported cases by the KCDC and the line list provided by the Seoul Metropolitan Government.}
Using line list, we reconstructed incidence for local $I_t^{\textrm{local}}$ and imported $I_t^{\textrm{imported}}$ cases separately based on the method described in the main text. Then, we estimated the time-dependent reproduction number via $\mathcal R_t = I_t^{\textrm{local}}/\sum_{k=1}^{14} I_{t-k} w_k$, where $I_t=I_t^{\textrm{local}}+I_t^{\textrm{imported}}$. We did not account for changes in testing criteria in this analysis.
The line lists were obtained from \url{http://news.seoul.go.kr/welfare/archives/513105}.
}
\end{figure}
